### 2015-02-06 cav-2015-tex/rw.tex
Did some cleanup in the related works section.

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}. However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.

\noindent\textbf{Bounded Model Checking}
Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition. The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis. Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis. By extension, the bounded reference models used in BMC methods are generally not complete. Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.

\noindent\textbf{Symbolic Heap Representations}
Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries. By introducing certain heuristics and approximations, the computational burden can be greatly reduced, at the cost of precision. Since the problem of weeding out false positives can be at least as difficult as the program analysis itself, there has been a renewed interest in more precise heap representations. However, these newer methods generally err on the side of under-approximation, producing an analysis that is not complete.

Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded. However, GSE does not offer a mechanism for representing the set of heaps along an execution path as a unified symbolic value. As a result GSE does not produce a path condition representing the complete set of inputs for a given execution path, negating a significant advantage of symbolic execution. The work presented here overcomes this limitation by using symbolic values to represent the heap.

A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps. However, none of these methods provide guarantees about the precision of the analysis performed, nor is it obvious that such guarantees are possible.

>>>>

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in~\cite{Elkarablieh:2009}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about more complicated examples. However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.

\noindent\textbf{Bounded Model Checking}
Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition. The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis. Many BMC methods include a model for reasoning about references, including those described in~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis. By extension, the bounded reference models used in BMC methods are generally not complete. Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.

\noindent\textbf{Other Symbolic Heap Representations}
%Due to technological limitations, many early symbolic heap representations focused on reducing the computational complexity of dereferencing queries. By introducing certain heuristics and approximations, the computational burden can be greatly reduced, at the cost of precision. Since the problem of weeding out false positives can be at least as difficult as the program analysis itself, there has been a renewed interest in more precise heap representations. However, these newer methods generally err on the side of under-approximation, producing an analysis that is not complete.
%
%Several GSE techniques~\cite{GSE03,KiasanKunit} form an exception to this rule, presenting an input heap model that is unconstrained and unbounded. However, GSE does not offer a mechanism for representing the set of heaps along an execution path as a unified symbolic value. As a result GSE does not produce a path condition representing the complete set of inputs for a given execution path, negating a significant advantage of symbolic execution. The work presented here overcomes this limitation by using symbolic values to represent the heap.
A number of constraint-based programming techniques are capable of reasoning about heaps~\cite{Degrave:2010,Charreteur:2009,Albert:2013}. Most notably, the technique in~\cite{Albert:2013} is capable of reasoning about dereferencing operations in a per-path set of unknown input heaps. However, none of these methods provide guarantees about the precision of the analysis performed, nor is it clear whether such guarantees are possible.
